---
title: "2019 Nutrient Analysis - Bible Hill"
author: "Emily G. Mantin"
date: "May 1, 2020"
output:
  html_document:
    toc: yes
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Miscanthus 

## Nutrient Analysis

### Nitrogen Content

Miscanthus biomass samples were collected for nutrient analysis from the Bible Hill field site on 01 October 2019.  Mean nitrogen content of Miscanthus plants was 


```{r (bh_N), echo=FALSE, warning=FALSE}
library(pander)

na <- read.table("2020-04-16_Nutrient Analysis_2.0.csv", header = TRUE,
                 sep = ",")
bh_N <- as.data.frame(na[1:16, c(2,5)])       ## Bible Hill Nitrogen Content
attach(bh_N)
model1 <- lm(N..plant ~ Treatment)
mod1.aov <- anova(model1)
panderOptions('missing', '')
pander(mod1.aov, caption = "ANOVA results of mean nitrogen content per plant (g N plant^-1^) in Miscanthus biomass collected on 01 October 2019 from Bible Hill, NS.")

```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
