---
title: "2019 Miscanthus Nutrient Analysis - Bible Hill"
author: "Emily G. Mantin"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Nutrient Analysis

Miscanthus shoot samples were collected in the fall for nutrient analysis.  Shoots were cut approximately 5 cm above ground level and placed in labelled paper bags.  Samples were placed in a drying oven (VWR Signature^TM^)  

## Nitrogen Content

```{r, echo=FALSE, warning=FALSE}
library(pander)

na <- read.table("2020-04-16_Nutrient Analysis_2.0.csv", header = TRUE,
                 sep = ",")

bh_NP.tab <- as.data.frame(na[1:16, c(2,5:7)])

bh_NP.tab2 <- as.data.frame(bh_NP.tab[, -3])

sum.table <- aggregate(bh_NP.tab2[, 2:3], list(bh_NP.tab2$Treatment), FUN = "mean")

names(sum.table)[1] <- "Treatment"
names(sum.table)[2] <- "Nitrogen Content (g N plant^-1^)"
names(sum.table)[3] <- "Phosphorus Content (g P plant^-1^)"

panderOptions('missing', '')
pander(sum.table, caption = "Mean values of nitrogen and phosphorus content measured in the fall of the establishment year (2019).")
```




```{r (bh_N), echo=FALSE, warning=FALSE}
library(pander)

na <- read.table("2020-04-16_Nutrient Analysis_2.0.csv", header = TRUE,
                 sep = ",")
bh_N <- as.data.frame(na[1:16, c(2,5)])       ## Bible Hill Nitrogen Content
attach(bh_N)
model1 <- lm(N..plant ~ Treatment)
mod1.aov <- anova(model1)
panderOptions('missing', '')
pander(mod1.aov, caption = "ANOVA results of mean nitrogen content per plant (g N plant^-1^) in Miscanthus biomass collected on 01 October 2019 from Bible Hill, NS.", add.significance.stars = TRUE)

```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
